How to Analyze Build Logs --- A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-27 tse-paper/content.tex
update graphics and pbe partially successful listing, include all notes for me from last meeting

% when we argue about this later we leave out the middle so A and B
% match.
whe then say that the long tail benefits from the generic
% solution.
Yes all benefit, but I think it's simpler like this.
\begin{figure}[tbhp]
		\centering
		\includegraphics[width=\columnwidth, trim={1.1cm 0.4cm
		1.5cm 0.5cm},
		clip]{img/lit-sur/log_producer_annotated.pdf}
		\caption{Frequency of supported log producers.}
		\label{fig:litsur:log_producer}
\end{figure}

@@

	\item Successful retrieval = $\mathit{true}\ \mathit{iff}\
	\mathit{Recall} = 1, \mathit{false\ otherwise}\vspace{0.1cm}$

	We define a successful retrieval as one where all desired
	lines were extracted, therefore when recall is one.
  % TODO introduce partially successful and (new) unsuccessful
\end{itemize}

@@

\lstset{
  language=,
  morekeywords={Test, Output, Desired},
  keywordstyle=\textbf,
	frame=single
}
\begin{figure}[!t]
  \centering
  \begin{lstlisting}[breaklines=true]
Test Output:
Error: Invalid CSS after "2.3em": expected expression (e.g.
1px, bold), was ";"
	on line 86 of sass/components/dropdown.sass
Desired Test Output:
Error: Invalid CSS after "2.3em": expected expression (e.g.
1px, bold), was ";"
	on line 86 of sass/components/dropdown.sass
	from line 5 of sass/components/_all.sass
	from line 6 of bulma.sass
  \end{lstlisting}
  \caption{Example for a partially successful retrieval
  (PBE retrieved only
  two of the four targeted lines).}
  \label{lst:pbe-unsuccessful}
\end{figure}

@@

% actually, we could cut this figure and move it's explanation
% to the next one (this is an aggregation of the next one)
% however, having them separate eases the entry into the results a bit
% and we have explanation of the categories before the more complicated
% aspect of the change with more structural categories
\Cref{fig:failure-reason-PBE} shows the results of chunk
retrieval with PBE.
It shows how many of the retrieval runs were successful or
partially successful, as well as the number of runs where the
synthesized program did not match on the analyzed build log or where
no program could be synthesized.
% The last two results stem from the regular expressions and their
% synthesis, therefore only apply to PBE.
Out of the overall 400 runs, 5 per each one of the 80 example
sets, PBE extracted all desired lines successfully in 138 cases.
In 59 cases, PBE could synthesize a regular expression program, though
it did not match on the test build log.
In 30 cases, the synthesized program only extracted a
subset of the desired lines.
For these 30 cases, the average recall
was 28\%.
\Cref{lst:pbe-unsuccessful} shows how an example of such
an \emph{partially successful retrieval} looks like.
In it, the synthesized program only
retrieved two of the four targeted lines.
In 173 of the 400 cases
could PROSE not synthesize a program consistent with all of the training
examples.

@@

\Cref{fig:results-CTS} shows violin plots
of the precision,
recall, and F$_{1}$-score of the chunk retrieval runs with CTS.
%The black horizontal lines show the average of these measurements.

@@

\Cref{fig:results-KWS} shows violin plots
of the precision,
recall, and F$_{1}$-score of the chunk retrieval runs with KWS.
%The black horizontal lines show the average of these measurements.

@@

\begin{table}[tbp]
\resizebox{\columnwidth}{!}{%
\centering
\begin{tabular}{llll}
  \toprule
  & \textbf{PBE} & \textbf{CTS} & \textbf{KWS} \\
  \midrule
  \textbf{Structural categories} & 1 & less is better & \makecell[l]{best
  1 \\
  multiple okay} \\
  \midrule
  \textbf{Training set size} & 2 & no influence & 2 \\
    \midrule
  \textbf{Precision} & \makecell[l]{high \\ (if synthesis succeeds)} &
  medium &
  low \\
    \midrule
  \textbf{Recall} & \makecell[l]{high \\ (if synthesis succeeds)} &
  medium &
  high \\
    \midrule
  \makecell[l]{\textbf{Confidence in} \\ \textbf{Output correctness}}
  & high & low &
  \makecell[l]{low (precision) \\ high (recall)} \\	\midrule
  \textbf{Output consumer} & program & human & human \\
  \bottomrule
\end{tabular}%
}
\caption{Recommendations for each of the investigated chunk retrieval
techniques.}
\label{tab:single-technique-recommendations}
\end{table}

@@

% we can't just have a paragraph in a scientific paper start with
% Caveat, I think ;-) Also, we should say why we THINK this is not
%the case.
% Otherwise we weaken our work unduly
% Of course we can! xD
% Agree with the rest.
It's in TtV, quite close actually
% so I'll comment this out
% also #moreselling :D
% \textbf{Caveat!}
% This is a preliminary hypothesis based on the results
% from our comparison study.
% The recommendations could therefore be
% influenced by idiosyncrasies of our specific implementation of the
% chunk retrieval techniques as well as the \emph{LogChunks}
% data set.

@@

\textbf{Comparison with more Chunk Retrieval Techniques.}
This
paper investigates the three chunk retrieval techniques PBE, CTS, and
KWS\@.
Our study design can be reused to evaluate other build log
analysis techniques, such as the diff and information retrieval
approach by Amar et al.~\cite{amar2019mining}.
% TODO: mention an actual chunk retrieval technique from the survey
% if possible

@@

\section{Conclusion}
\label{sec:conclusion-fw}
% TODO CARO conclusion should be a bit longer and a little bit more in
% detail.
%Mention general accuracy measures (techniques performed
% up to in F1 score, which is x times better than RLR)
The goal of this paper is to support practitioners and researchers in
their decision on how to analyze build logs.
To this end, we first
conducted a systematic mapping study to map out the available build
log analysis techniques.
We then
implemented three promising chunk retrieval techniques and compared
their performance on the \emph{LogChunks} data set.
Our results show
that the structural representation of the targeted information in the
build logs is the main factor to consider when choosing a suitable
technique.
Secondary factors are the desired confidence in recall and
precision of the produced output and whether precision or recall is
more important for the task at hand.

>>>>

% TODO Caro: adapt as discussed
\begin{figure}[tbhp]
		\centering
		\includegraphics[width=\columnwidth, trim={1.1cm 0.4cm
		1.5cm 0.5cm},
		clip]{img/lit-sur/log_producer_annotated.pdf}
		\caption{Frequency of supported log producers.}
		\label{fig:litsur:log_producer}
\end{figure}

@@

	% actually that is now giving recall another (nicer) name
	% improved if we just talk about recall later?
	\item Successful retrieval = $\mathit{true}\ \mathit{iff}\
	\mathit{Recall} = 1, \mathit{false\ otherwise}\vspace{0.1cm}$
	Partially Successful retrieval = $\mathit{true}\ \mathit{iff}\
	0 < \mathit{Recall} < 1, \mathit{false\ otherwise}\vspace{0.1cm}$
	Unsuccessful retrieval = $\mathit{true}\ \mathit{iff}\
	\mathit{Recall} = 0, \mathit{false\ otherwise}\vspace{0.1cm}$

	We define a successful retrieval as one where all desired
	lines were extracted, therefore when recall is one.
	A retrieval is partially successful if at least some of the
	desired lines were extracted.
	If the retrieved lines contain none of the desired lines
	a retrieval was unsuccessful.
\end{itemize}

@@

\lstset{
  language=,
  morekeywords={Test, Output, Desired},
  keywordstyle=\textbf,
	frame=single
}
\begin{figure}[!t]
  \centering
\begin{subfigure}[b]{\columnwidth}
  \begin{lstlisting}[breaklines=true,frame=tlr]
[0K$ test/sass-compile-tester.sh
  \end{lstlisting}
  \vspace{-\baselineskip}
  \begin{lstlisting}[backgroundcolor=\color{Yellow!60},breaklines=true,frame=rl]
Error: Invalid CSS after "2.3em": expected expression (e.g.
1px, bold), was ";"
	on line 86 of sass/components/dropdown.
  \end{lstlisting}
  \vspace{-\baselineskip}
  \begin{lstlisting}[breaklines=true,frame=blr]
	from line 5 of sass/components/_all.sass
  \end{lstlisting}
	\caption{Yellow: chunk retrieval output ($RetrievedLines$)}
	\label{lst:pbe-part-success-output}
\end{subfigure}

\begin{subfigure}[b]{\columnwidth}
  \begin{lstlisting}[breaklines=true,frame=tlr]
[0K$ test/sass-compile-tester.sh
  \end{lstlisting}
  \vspace{-\baselineskip}
  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
Error: Invalid CSS after "2.3em": expected expression (e.g.
1px, bold), was ";"
	on line 86 of sass/components/dropdown.sass
	from line 5 of sass/components/_all.sass
	from line 6 of bulma.sass
  \end{lstlisting}
  \vspace{-\baselineskip}
  \begin{lstlisting}[breaklines=true,frame=blr]
  Use --trace for backtrace.
  \end{lstlisting}
	\caption{Blue: targeted chunk ($DesiredLines$)}
	\label{lst:pbe-part-success-desired}
\end{subfigure}
  \caption{Example for a partially successful retrieval
  (PBE retrieved only
  two of the four targeted lines).}
  \label{lst:pbe-unsuccessful}
\end{figure}

@@

% actually, we could cut this figure and move it's explanation
% to the next one (this is an aggregation of the next one)
% however, having them separate eases the entry into the results a bit
% and we have explanation of the categories before the more complicated
% aspect of the change with more structural categories
\Cref{fig:failure-reason-PBE} shows the results of chunk
retrieval with PBE.
It shows how many of the retrieval runs were successful or
partially successful, as well as the number of runs where the
synthesized program did not match on the analyzed build log or where
no program could be synthesized.
% The last two results stem from the regular expressions and their
% synthesis, therefore only apply to PBE.
Out of the overall 400 runs, 5 per each one of the 80 example
sets, PBE extracted all desired lines successfully in 138 cases.
In 18 cases, the synthesized program only extracted a
subset of the desired lines, while in 12 cases it extracted none of
the desired lines.
For these 18 partially successful, the average recall
was 47\%.
\Cref{lst:pbe-unsuccessful} shows how an example of such
a partially successful retrieval looks like.
In it, the synthesized program only
retrieved two (\Cref{lst:pbe-part-success-output})
of the four (\Cref{lst:pbe-part-success-desired}) targeted lines.
In 59 cases, PBE could synthesize a regular expression program, though
it did not match on the test build log.
In 173 of the 400 cases
could PROSE not synthesize a program consistent with all of the training
examples.

@@

\Cref{fig:results-CTS} shows violin plots
of the precision,
recall, and F$_{1}$-score of the chunk retrieval runs with CTS.
The black horizontal lines show the average of these measurements.
If the figure shows no violin plot for a category, we only have one
data point or all data points have the same value.

@@

\Cref{fig:results-KWS} shows violin plots
of the precision,
recall, and F$_{1}$-score of the chunk retrieval runs with KWS.
The black horizontal lines show the average of these measurements.
If the figure shows no violin plot for a category, we only have one
data point or all data points have the same value.

@@

% capitalized headings / left title column
% tried it out, I think it looks better with the rest lowercase
\begin{table}[tbp]
\resizebox{\columnwidth}{!}{%
\centering
\begin{tabular}{llll}
  \toprule
  & \textbf{PBE} & \textbf{CTS} & \textbf{KWS} \\
  \midrule
  \textbf{Structural Categories} & 1 & less is better & \makecell[l]{best
  1 \\
  multiple okay} \\
  \midrule
  \textbf{Training Set Size} & 2 & no influence & 2 \\
    \midrule
  \textbf{Precision} & \makecell[l]{high \\ (if synthesis succeeds)} &
  medium &
  low \\
    \midrule
  \textbf{Recall} & \makecell[l]{high \\ (if synthesis succeeds)} &
  medium &
  high \\
    \midrule
  \makecell[l]{\textbf{Confidence in} \\ \textbf{Output Correctness}}
  & high & low &
  \makecell[l]{low (precision) \\ high (recall)} \\	\midrule
  \textbf{Output Consumer} & program & human & human \\
  \bottomrule
\end{tabular}%
}
\caption{Recommendations for each of the investigated chunk retrieval
techniques.}
\label{tab:single-technique-recommendations}
\end{table}

@@

% we can't just have a paragraph in a scientific paper start with
% Caveat, I think ;-) Also, we should say why we THINK this is not
%the case.
% Otherwise we weaken our work unduly
% Of course we can! xD
% Agree with the rest.
% It's in TtV, quite close actually
% so I'll comment this out
% also #moreselling :D
% \textbf{Caveat!}
% This is a preliminary hypothesis based on the results
% from our comparison study.
% The recommendations could therefore be
% influenced by idiosyncrasies of our specific implementation of the
% chunk retrieval techniques as well as the \emph{LogChunks}
% data set.

@@

\textbf{Comparison with more Chunk Retrieval Techniques.}
This
paper investigates the three chunk retrieval techniques PBE, CTS, and
KWS\@.
Our study design can be reused to evaluate other build log
analysis techniques, such as the parser Tomassi et al.
used to create
BugSwarm~\cite{tomassi2019bugswarm} or the regex-based approach
Beller et al.
used to create TravisTorrent~\cite{beller2017oops}.

@@

\section{Conclusion}
\label{sec:conclusion-fw}
% TODO CARO conclusion should be a bit longer and a little bit more in
% detail.
 TODO Mention general accuracy measures (techniques performed
up to in F1 score, which is x times better than RLR)
The goal of this paper is to support practitioners and researchers in
their decision on how to analyze build logs.
To this end, we first
conducted a systematic mapping study to map out the available build
log analysis techniques.
We then
implemented three promising chunk retrieval techniques and compared
their performance on the \emph{LogChunks} data set.
Our results show
that the structural representation of the targeted information in the
build logs is the main factor to consider when choosing a suitable
technique.
Secondary factors are the desired confidence in recall and
precision of the produced output and whether precision or recall is
more important for the task at hand.
